---
title: "Specialist Haemostasis IQC Report"
author: "Stephen MacDonald"
date: "June 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the Internal Quality Control analysis document for the Specialist Haemostasis department, Cambridge University Hospital Foundation Trust, Cambridge, UK.

## Summary of performance of all assays 

- same as ECAT do for a high level overview of results. ? use a heatmap to show what is god and what isnt. Break it down by:
assay, analyser, qc material

## Exploratory Analysis of the previous month's IQC

Below are the initial exploratory statistics for the data for the preceding month.
SM - upload data from the last month to this folder
joyplots to detect variance of all QC over time - checks the first assumption that all QC are running to a normal distribution
Boxplots using ggplot to show variance of results of each QC?
```{r, echo=FALSE, warning=FALSE, fig.width=3}
library(ggplot2)
ggplot(data=iris, aes(x=Species, y=Petal.Width)) + geom_boxplot()
```


## QC Charts
SM - can you use par mfrow to get 

## Time Series and Trend Analysis
```{r}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

```{r}
library(d3heatmap)
d3heatmap(mtcars, scale="column", colors="Blues")
```



## change in six sigma perfromance of the assay over time


```{r cars}
summary(cars)
```

## Including Plots


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
